\section{Related Work}
  Webs-of-trust can be used as a basis for trust \cite{wot}. PGP \cite{pgp} implements one and Freenet \cite{freenet}
  another, built against spam. Ways of calculating trust towards distant nodes are proposed in \cite{mui,beta}. In \cite{vpc},
  trust is calculated hierarchically. CA- and Byzantine-based \cite{byzantine} PKIs \cite{pki} require central trusted third
  parties or at least authenticated membership. \cite{fire}, \cite{core}, \cite{ghkkw}, \cite{rk} do not prove any Sybil
  resilience. All these systems do not define trust financially.

  To discourage Sybil attacks, Beaver \cite{beaver} relies on fees, something we avoid.  Our motivating application is
  OpenBazaar, where transitive financial trust has previously been explored in \cite{dionyziz}. We are strongly inspired by
  \cite{kmrs} who give a sociological justification for the central design choice of identifying trust with risk. We
  appreciate \cite{davis}, which proposes a financial trust system with transitivity, with trust defined as lines-of-credit,
  similar to us. We extended their work by using the blockchain for automated proofs-of-risk, a feature not available to them
  at the time.

  Our Conservative strategy and Transitive Game remind \cite{iou} which is also financially transitive and is used by
  \cite{ripple}, \cite{stellar}. IOUs in those correspond to our edges of trust reversed. The critical difference
  is that our trust is expressed in a global currency and there is no money-as-debt. Furthermore, we proved that trust and
  maximum flows are equivalent, a direction not explored in their papers.
